### 2014-08-25 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Rename figures

Part of the function of the Fire Research Division at NIST is to develop and apply technology, measurements, and standards to improve the understanding of the behavior, prevention, and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response. NIST has previously used the Fire Dynamics Simulator (FDS) fire model to provide insight into the fire development and thermal conditions of fires that have resulted in line of duty deaths (LODDs)~\cite{Madrzykowski:1,Iowa,Texas,Bryner:Charleston,barowy:texas}. The objective of these studies has been to improve the safety and effectiveness of firefighters.

@@

\begin{figure}[!ht]
\includegraphics[width=3.20in]{../Figures/post_exterior_front}
\hfill
\includegraphics[width=3.20in]{../Figures/post_exterior_rear}
\caption{Front (left) and rear (right) exterior of the structure after the incident.}
\label{fig:post_exterior}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6.5in]{../Figures/Top_Floor_Metric}
\caption[Dimensioned drawing of the second floor.]{Dimensioned drawing of the second floor. The measurements are accurate to within 15~cm (6~in).}
\label{fig:drawing_second_floor}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6.5in]{../Figures/Ground_Floor_Metric}
\caption[Dimensioned drawing of the first floor.]{Dimensioned drawing of the first floor. The measurements are accurate to within 15~cm (6~in).}
\label{fig:drawing_first_floor}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6.5in]{../Figures/Sub_Level_1_Metric}
\caption[Dimensioned drawing of the basement.]{Dimensioned drawing of the basement. The measurements are accurate to within 15~cm (6~in).}
\label{fig:drawing_basement}
\end{figure}

>>>>

Part of the function of the Fire Research Division at the National Institute of Standars and Technology (NIST) is to develop and apply technology, measurements, and standards to improve the understanding of the behavior, prevention, and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response. NIST has previously used the Fire Dynamics Simulator (FDS) fire model to provide insight into the fire development and thermal conditions of fires that have resulted in line of duty deaths (LODDs)~\cite{Madrzykowski:1,Iowa,Texas,Bryner:Charleston,barowy:texas}. The objective of these studies has been to improve the safety and effectiveness of firefighters.

@@

\begin{figure}[!ht]
\includegraphics[width=3.20in]{../Figures/Post_Exterior_Front}
\hfill
\includegraphics[width=3.20in]{../Figures/Post_Exterior_Rear}
\caption{Front (left) and rear (right) exterior of the structure after the incident.}
\label{fig:post_exterior}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6.5in]{../Figures/Drawing_Second_Floor_Metric}
\caption[Dimensioned drawing of the second floor.]{Dimensioned drawing of the second floor. The measurements are accurate to within 15~cm (6~in).}
\label{fig:drawing_second_floor}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6.5in]{../Figures/Drawing_First_Floor_Metric}
\caption[Dimensioned drawing of the first floor.]{Dimensioned drawing of the first floor. The measurements are accurate to within 15~cm (6~in).}
\label{fig:drawing_first_floor}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6.5in]{../Figures/Drawing_Basement_Metric}
\caption[Dimensioned drawing of the basement.]{Dimensioned drawing of the basement. The measurements are accurate to within 15~cm (6~in).}
\label{fig:drawing_basement}
\end{figure}
